\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{fancyhdr}
\usepackage{enumitem}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\renewcommand{\headrulewidth}{0.4pt} % Horizontal line below the header

\begin{document}

% Main title
\begin{center}
    \Large \textbf{Activity Week 9 Updates} \\
    \vspace{0.2cm}
    \normalsize Math-115-02 Activity Section\\
\end{center}
\section*{Introduction}
Hello everyone, congrats on finishing week 9! \\
I wanted to give everyone a grade update and helpful information.\\
\\
We’ve been doing our best to develop a better and more understandable 
system so you guys can see exactly how everything affects your grade 
and how the activity class grade is combined with the lecture 
component’s grade! I have talked about this a couple of times in 
activity but now here it is in writing in case there is any confusion. 
\\\\
Overall, nothing much was changed, 
we just put all the activity component into Canvas.
Everything is for your benifit so theres nothing to worry about!
%\section*{Helpful Resources}
%\subsection*{Activity Archive}
\section*{Gradebook Updates}

\begin{itemize}
    \item Activity Warm-ups and Lecture Warm-ups are both 
          counted to the 10\% Warm up total. 
    \item Everything else in Activity, Lecture present points, and 
    Lecture group work are part of the 20\% 
    Activity/Engagement portion of your grade
    \item I will do my best to update the Activity grades on a weekly basis, 
but if you ever need to talk about your grade, see how your grade 
can change, always feel free to find me in the stem lab during 
office hours or email me!
\end{itemize}
\vspace{20cm}
\section*{Activity Grade Updates}
\begin{itemize}
    \item As a reminder, the activity component is worth roughly 20 of your overall grade, so always try and show up.
    \item Activity component participation, warm-ups, assignments, and bonus points are now on Canvas!
        Here is the grade breakdown for the activity component again:
        \begin{itemize}
            \item *1 points per class attendance
            \item *2 for engagement
            \item *1 points entry/exit tickets
            \item *1-5 points take-home homework/bonus activity
            \item *1 point for visiting STEM Lab, TA, or LA office 
                hour (max 2 per week letting your TA or LA know you attended)
            \item *1 point for studying with another student outside of class 
            (max 2 per week providing some sort of evidence such as a screenshot/picture of the group.)
            \item *1 point for outside-of-class activity 
            (max 2 per week, e.g. making an exam study plan, reflection assignment).
            \item *these values might be changed over the semester if I need to adjust the schedule or homework
        \end{itemize}

\end{itemize}
\section*{Activity Archive}
\begin{itemize}
    \item start
\end{itemize}
\section*{Class Discord}
\begin{itemize}
    \item Johnny made a class Discord a while ago, here 
    is the link again to join! 
    \item Talk your classmates, and 
    ask our LAs questions quicker than email! 
    \item The professor andz I are not in the server whatsoever.
    \item You can always let Johnny know about something if  \\
    want the message relayed to the professor or me!
    \item Please do be respectful and practice online etiquette!
    \item Math–155E-2 Discord Link: xxxxxxxxxxxxxx
\end{itemize}


\section*{Want to make up points?}
\begin{itemize}
    \item Visit the stem lab for 1 point per visit for up to 2 points per week, they can really add up and myself and others can help and support you! I get a digital record of who shows up so there is no need to tell us when you go, I’ll integrate that into your grade
    \item I will allow you to submit previous homework assignments of mine late for no reduced points, but please be responsible, I would highly recommend you complete them on pace with the rest of the class, so you don’t get too behind or too lost.  
    \item Quite often I will hand out bonus activities that are entirely optional to finish outside of class, but if you do, they count for bonus points as well
\end{itemize}
\section*{Questions?}
\begin{itemize}
\item          There is the Student QA section in canvas, post any question you have for any of us, whether it be assignments, making up points, confused about homework, etc. Be sure to never post any personal information please, everyone will be able to see what you post.
\item         As always, you are always welcome to visit any of us during office hours and to email us
\end{itemize}


\end{document}